Assessment and implementation of resource road simulation methods for projection of cumulative effects of disturbance on wildlife

### 2023-04-13 analysis/paper/paper.Rmd
Add fig results for real cutblocks only Only added the table and checked the difference in the figure

```{r get-data}
# load csv
meanTable <- read.csv(here(data_path_drvd, "mean_table.csv"))

matchData <- read.csv(here(data_path_drvd, "agree_table.csv"))

>>>>

```{r get-data}
# load csv
meanTable <- read.csv(here(data_path_drvd, "mean_table.csv"))
meanTableRealCuts <- read.csv(here(data_path_drvd,"../TSA27_real_cuts",
                                   "mean_table.csv"))
matchData <- read.csv(here(data_path_drvd, "agree_table.csv"))
